%% start of file `template.tex'.
%% Copyright 2006-2010 Xavier Danaux (xdanaux@gmail.com).
%% Copyright 2010-2011 Mark Liu (markwayneliu@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}

\usepackage{verbatim}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\setlength{\hintscolumnwidth}{3.2cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths


% personal data
\firstname{Johanna}
\familyname{Hansen}
\address{10 Bell Tower Lane}{Woods Hole, MA 02543}    % optional, remove the line if not wanted
\mobile{979.240.4446}                    % optional, remove the line if not wanted
\email{jhansen@whoi.edu}                      % optional, remove the line if not wanted
%\extrainfo{\url{http://markliu.me}} % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Technical Qualifications Summary}
\cvline{}{Digital Signal Processing, Hardware/Software Integration, Embedded Systems,
Python, Numpy, Matlab, C, DMM, Scopes, Matlab, C++, QT, 
\LaTeX{}, GIS, Telecommunications Infrastructure, Computer Networking}

\section{Education}
\cventry{2012--2015}{MS, Electrical Engineering}{University of Texas, San Antonio}{San Antonio, TX}{}{}
\cvline{Concentration}{\small Digital Signal Processing}
\cvline{Coursework}{\small Digital Signal Processing, Digital Filters, Graph Theory, 
Fundamentals of Machine Learning, Remote Sensing}
\cventry{2007--2011}{BS, Electrical Engineering}{Texas State University}{San Marcos, TX}{}{}
\cvline{Concentration}{\small Communications and Networking}
\cvline{Coursework}{\small Networking, Data Compression and Error Coding, 
    Wireless Communications, Communication Theory, 
Microprocessors, Digital Design, Electronics I/II, Digital Signal Processing, 
Circuit Analysis, Electromagnetism, Systems and Signals}
\cventry{2007--2011}{BS, Geography}{Texas State University}{San Marcos, TX}{}{}
\cvline{Concentration}{\small Resource and Environmental Science}
\cvline{Coursework}{\small GIS, Water Resources, Earth Science, Physical Geography, Quantitative Data Analysis}
\section{Professional Development}
\cvline{Courses}{Technical Writing, Project Management, Proposal Writing,Promoting to Research and Development, Technical Presentations, Geophysics to Detect Solutional Features}
\cvline{Conferences}{2013 SciPY - Conference and Tutorials, Machine Learning and Geospatial Track, 2013 PyTexas}
\cvline{Presentations}{Dynamics Estimation for AUVs in the Absence of DVL Bottom-lock using ADCP Aided State Estimation - Lash Medagoda, 2014 WHOI Technical Employee Presentations}


\section{Experience}

\cventry{Jan 2014--Present}{Engineer II}{Woods Hole Oceanographic Institution}{Woods Hole, MA}{}
{
Electrical/Software Systems Engineer for the Sentry AUV team in the Applied Ocean Physics 
and Engineering Department. Worked as part of the operations team to Write, modify, 
and debug data processing, vehicle control, and device driver software in python, 
Matlab, C, C++, and BASH both in the lab and at sea.
    \begin{itemize}
        \item Assist in maintaining data storage, processing, and network architecture
        \item Process geophysical, acoustic, navigation, and photo data
        \item Assist in all aspects of at-sea operations
        \item Develop documentation for both internal and external use
    \end{itemize}
}

\cventry{Jan 2012-Jan 2014}{Engineer}{Southwest Research Institute (SwRI)}{San Antonio, TX}{}
{
    Primary developer and system integrator on project to build remote sensor that utilized ultrasonic
transducers and video the map culverts for the FHWA. 
     \begin{itemize}
        \item Built sensor consisting of 40 kHz transducers, DSP board, camera, IMU, and Gumstix Computer with a custom Angstrom Linux Distribution. 
        \item Sampled, filtered, and normalized incoming acoustic data in C on a 
            PIC micro-controller.
        \item Developed wxpython graphical user interface in Windows for wireless control, 
            status updates, and data transmission from sensor. 
        \item Principal Investigator for Internal Research Project to implement intelligent propulsion
            system using low-cost acoustic sensing. 
    \end{itemize}
    }

    \cventry{Jan 2011--Dec 2011}{Engineering Coop}{Lower Colorado River Authority (LCRA)}{Austin, TX}{}
    {Year-long coop student for the telecommunications department while 
maintaining status as a full-time, undergraduate student.
 \begin{itemize}
        \item Designed and configured SONET, optical fiber, Ethernet, and microwave systems
            critical communication infrastructure including power generation/distribution, dam and 
            irrigation control, and emergency response coordination. 
        \item Project lead for pilot irrigation control system using networked
            900 MHz Radios. 
        \item Assessed fiber installations using OTDR for future expansion planning.
    \end{itemize}
}

\cventry{Jan 2010--Dec 2010}{Teaching/Lab Assistant}{Texas State University}{San Marcos, TX}{}
{Assisted with Signals and Systems, Electronics, Microprocessors, and 
Engineering Management Courses and labs as an undergraduate}

\cventry{Aug 2008--Aug 2010}{Technical Support}{AirGenerate}{Houston, TX}{}
{Provided Remote Technical Support via email and phone for Heat-Pump Hot Water Heater Start-up Company}

\section{Publications}
\cventry{2014}{Transportation Research Board 93rd Annual Meeting}{The Ultrasonic Culvert Inspection System (UCIS): A Low-Cost Device for Conduit Inspection}{Hansen, Johanna, Wilden, Gregory, Abbott, Ben, Green, Ronald}{}{}

\section{Oceanographic Research Cruises}
\cvline{2014-FSM}{Utilized first research cruise to develop system understanding. Began work on
Reson Multibeam Driver. Initiated work to improve data management practices. Successfully
conducted pre/post dives.}
\cvline{2014-Cordes}{Worked as primary software team member for pre/post dive. Deployed new Reson 
Driver for automated control of the multibeam sonar. Implemented multi-threaded
photo processing pipeline so that photos could be produced within minutes rather than hours. 
Produced several scripts to ease pre-dive tasks.
Performed data management tasks and interacted with science and documentary team.}
\cvline{2014-Glazer}{Worked as primary software team member in tandem with electrical and
mechanical teams to troubleshoot many hardware failures. Worked closely with EL and 
Chief Scientist to provide valuable data processing for science.}
\cvline{2014-Kinsey}{Served as Sentry software contact for Optical Communication
System integration for two successful dives. Developed acoustic and optical geolocation
capability with guidance of EL and graduate student. Troubleshot DVL, Avtrak, Optode
installations and produced technical reports. Provided training for new staff in pre/post
dive process.}




\section{Organizations}
\cvline{IEEE}{Signal Processing, Geoscience and Remote Sensing, Ocean Memberships}
\cvline{CCYP}{Cape Cod Young Professionals Member}
\cvline{CTO}{2013 South-Central CleanTech Open Incubator Judge, Austin TX}

\section{Activities}
\cvline{Gardening}{WHOI Gardener, SwRI Gardening Club - Founding Member and Club Secretary}
\cvline{SCUBA}{NAUI Master Scuba Diver, Diving for Science Certified}
\cvline{Other Hobbies}{Hiking, Backpacking, Traveling, Equestrian Sports, Paddleboarding, Kayaking}

\end{document}
